On the application of microwave acoustic resonant viral inactivation \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}

### 2020-06-17 documents/paper.tex
More teensy
Re-organized yet again, company too

We began experimentally by building a scaled version of [Mueller 2008]'s active antenna on FR4, using a CEL mosfet.

Optimizing S-parameter simulations of the feedback loop and negative-resistance device did not produce an accurate picture of the oscillator. While the phase and frequency response appeared to be excellent, the transient response painted a different picture:

[gnuplot transient sim here]

This immediately oscillated perfectly.

@@

\clearpage

{\Large Captain's Log, Supplemental}\\

@@

CEL did not supply a SPICE model for the GaAs FET device used in early prototypes. A FET was chosen because the a gate is ostensibly easier to bias than a base.

@@

[Polyfet 1998] describes a simple optimization method to synthesize a SPICE model; it would be useful.

However, since a Si-process device would be required for mass production anyhow, we decided to accept the difficulty in biasing and use a bipolar transistor.

@@

Simulating the oscillator with an AC sim using the manufacturer's S-parameters and QUCS' microstrip approximations [qucs/optimize\_filter\_1] intially appeared to yield good agreement with experiment. Peaks in the feedback voltage simulation corresponded approximately with peaks in the observed spectrum. [figures from LO prototype N].

However, unexpected dips and peaks were found with varactor tuning; and the tuning range was far smaller than expected.

A feedback loop filter design with apparently ideal phase and frequency properties was designed using this process; but the behavior of this oscillator did not correspond to reality.

\hspace*{-0.7cm}   \includegraphics[scale=0.6]{LO_2_pole_test.png}

@@

As of 0.0.20, QUCS' microstrip models are not yet compatible with transient simulations; and some improved filter designs required simulating coupling between more than two microstrips, which QUCS did not yet support natively. Coupling can be emulated by introducing discrete coupling capacitors

@@

In some situations (especially where the library has a permissive licence) perhaps it could be useful to consider packaging a complete, batteries-included 'known good' repository, either with the source of all the correct library versions included, or with a script to clone and compile the specific version used, and integrating all the libraries with the build system.

@@

In one example, many hours were spent because the enamel insulation on a bodge wire had not burned off completely in the solder joint, leading to a high-impedance connection.

@@

@@

>>>>

@@

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\Large Captain's Log, Supplemental}\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

CEL did not supply a SPICE model for the GaAs FET device used in early prototypes. A FET was originally because a gate is ostensibly easier to bias than a base; but this turned out to be unfounded.

@@

[Polyfet 1998] describes a simple optimization method to synthesize a SPICE model for an active device, and CEL appnote provides some details for GaAs devices.

@@

We began experimentally by building a scaled version of [Mueller 2008]'s active antenna crudely with copper tape, using a CEL [] FET.

We then manually tried a number of filter designs, using the manufacturer's S-parameters and QUCS' microstrip approximations. This intially appeared to yield good agreement with experiment. Peaks in the feedback voltage simulation corresponded approximately with peaks in the observed spectrum. [figures from LO prototype N].

A crude, inane, and extremely disorganized trial-and-error procedure was performed for many weeks. A wide variety of analytical methods for filter design were attempted, but simultaneously obtaining the correct phase shift and frequency response was somewhat difficult. The parasitic inductance of the varactors always seemed to destroy our most perfect creations.

An SIR filter has the added advantage of confusing epidemiologists greatly.

Eventually, QUCS, zonca/python-qucs, and scipy's basinhopper was used with the cost function somewhat similar to that described in [Kaplevich]:

\begin{verbatim}
    freq_coeff = 1
    phase_coeff = 1.5
    ratio_coeff = 0.5
    insertion_loss_coeff = 0.2

    frequency_cost = freq_coeff * (abs(desired_center_frequency-fb_peak_frequencies[0])/1e9)
    phase_cost = phase_coeff * abs(1.0 - phase_at_peak)
    ratio_cost = ratio_coeff * fb_peak_ratio
    insertion_loss_cost = insertion_loss_coeff*(1.0 - fb_peak_values[0])
    cost = frequency_cost + phase_cost + fb_peak_ratio + insertion_loss_cost
\end{verbatim}

Optimizing first for the high frequency, fixing the inductor and microstrip values, and then optimizing for the varactor values at the low frequency.

This produced a seemingly acceptable feedback loop:

\includegraphics[scale=1]{LO_2_pole_test.png}

However, when this was built, varactor tuning performance was abysmal, with hops and peaks; and the tuning range was far smaller than expected.

As of 0.0.20, QUCS' microstrip models are not yet compatible with transient simulations; and some improved filter designs required simulating coupling between more than two microstrips, which QUCS did not yet support natively.

\includegraphics[scale=0.5]{3d_spectrum_2.png}

@@

@@

In some situations (especially where the library has a permissive licence) perhaps it could be useful to consider packaging a complete, batteries-included 'known good' repository, either with the source of all the correct library versions included, or with a script to clone and compile the specific version used, integrating all the libraries with the build system.

@@

In one example in this project, many hours were wasted because the enamel insulation on a bodge wire had not burned off completely in the solder joint, leading to a high-impedance connection.

@@

Boundary-scan features might really help

The ability to almost immediately compare simulation to experiment was quite important.

@@

%\end{multicols}
